The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
funding for myself

\item Trilinos linear operators?
  TODO: Jean-Paul and Matthias

@@

\subsection{TODO: Linear operators with Payload and Trilinos}

TODO: Jean-Paul and Matthias

@@

>>>>

\item The \texttt{LinearOperator} class has been extended to fully support {\trilinos} solvers.

@@

\subsection{Extension of the \texttt{LinearOperator} class}

By introduction of an arbitrary \texttt{Payload} base class, the \texttt{LinearOperator} class can be extended to seamlessly exploit the native features and operations offered by external linear algebra libraries.
We have thus developed a \texttt{TrilinosPayload} class, through which full support for the suite of {\trilinos} parallel iterative solvers and preconditioners has been achieved.
In the case of the construction of an \texttt{inverse\_operator}, both \dealii's built in solvers and those offered by {\trilinos} can be selected.
This has been achieved by using the \texttt{Epetra\_Operator} as the basis for the \texttt{TrilinosPayload}, for which the result of both standard and composite operations involving forward (\texttt{Apply()}) and inverse (\texttt{ApplyInverse()}) matrix-vector multiplication are collated using lambda functions.
It is envisaged that, in the future, similar can be done for the {\petsc} iterative solvers.

An additional feature of the \texttt{LinearOperator} suite is the defintion of a \texttt{schur\_complement} operator, and its associated condensation and post-processing \texttt{PackagedOperation}s.
An operator representing the Schur complement of a block system can be declared and, though the delayed evaluation offered by \texttt{PackagedOperation}s, reused on any number of vector systems.

@@

D. Davydov was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).
